Poster Data Analysis

### 2018-09-10 notebooks/poster_analysis.Rmd
minor fixes and added table of mlst profiles per species

@@

@@

```{r}
test <- mic_data %>%
  select(-antres) %>%
  left_join(species_data, by = "id") %>%
  mutate(SMX_R = ifelse(SMX > 64, 1, 0),
         TMP_R = ifelse(TMP > 2, 1, 0),
         CIP_R = ifelse(CIP > 0.06, 1, 0),
         TET_R = ifelse(TET > 8, 1, 0),
         NAL_R = ifelse(NAL > 16, 1, 0),
         CTX_R = ifelse(CTX > 0.25, 1, 0),
         CHL_R = ifelse(CHL > 16, 1, 0),
         AMP_R = ifelse(AMP > 8, 1, 0),
         GEN_R = ifelse(GEN > 2, 1, 0)) %>%
  select(contains("_R"), species) %>%
  split(., f = .$species) %>%
  lapply(., function(x) select(x, -species))

corr_matrices <- lapply(test, function(x) create_corr_matrix(x)) %>%
  bind_rows(.id = "species")

>>>>

## Total percentage of isolates with detected acquired genes and mutant intrinsic genes

### Percent acquired genes
```{r}
resfinder_results %>%
  select(-c(id, type)) %>%
  mutate(total = rowSums(.),
         result = if_else(total != 0, 1, 0)) %>%
  group_by(result) %>%
  count() %>%
  ungroup() %>%
  mutate(result = if_else(result == 0, "Absent", "Present")) %>%
  spread(result, n) %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total * 100,2),
         lwr = round(get_binCI(Present, Total)[1], 2),
         upr = round(get_binCI(Present, Total)[2], 2))

### Percent mutations in intrinsic genes
```{r}
megares_results %>%
  select(-c(id, type, acrB)) %>%
  mutate(total = rowSums(., na.rm = TRUE),
         result = if_else(total != 0, 1, 0)) %>%
  group_by(result) %>%
  count() %>%
  ungroup() %>%
  mutate(result = if_else(result == 0, "Absent", "Present")) %>%
  spread(result, n) %>%
  mutate(Total = Present + Absent,
         Percent = round(Present/Total * 100,2),
         lwr = round(get_binCI(Present, Total)[1], 2),
         upr = round(get_binCI(Present, Total)[2], 2))
```

@@

### Number of sequence types per animal species
```{r}
total_ST_per_species <- mlst_per_species %>%
  group_by(species) %>%
  count()
total_ST_per_species
```

@@

```{r}
mic_per_species <- mic_data %>%
  select(-antres) %>%
  left_join(species_data, by = "id") %>%
  mutate(SMX_R = ifelse(SMX > 64, 1, 0),
         TMP_R = ifelse(TMP > 2, 1, 0),
         CIP_R = ifelse(CIP > 0.06, 1, 0),
         TET_R = ifelse(TET > 8, 1, 0),
         NAL_R = ifelse(NAL > 16, 1, 0),
         CTX_R = ifelse(CTX > 0.25, 1, 0),
         CHL_R = ifelse(CHL > 16, 1, 0),
         AMP_R = ifelse(AMP > 8, 1, 0),
         GEN_R = ifelse(GEN > 2, 1, 0)) %>%
  select(contains("_R"), species) %>%
  split(., f = .$species) %>%
  lapply(., function(x) select(x, -species))

corr_matrices <- lapply(mic_per_species, function(x) create_corr_matrix(x)) %>%
  bind_rows(.id = "species")
